**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2021-02-09 submission/manuscript.Rmd
Fromat text.

@@

\newpage
## Experimental procedures
### Sampling
Leaves of *C. nodosa* were sampled in a *C. nodosa* meadow in the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20} E) and in a *C. nodosa* meadow invaded by *C. cylindracea* in the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N, \ang{13;35;42} E). Thalli of *C. cylindracea* were sampled in the same *C. nodosa* invaded meadow in the Bay of Funtana and at a locality of only *C. cylindracea* located in the proximity of the invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics and metaproteomics were collected in two contrasting seasons, on 4 December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017 (metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and metaproteomics). During spring 2018, the *C. nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved [@Najdek2020]. In addition, as not enough DNA for both metagenomic and 16S RNA analysis were obtained during the sampling on 4 December 2017, an additional sampling on 14 December 2017 was carried out in the Bay of Funtana. Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with seawater from this site. Upon arrival to the laboratory, *C. nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *C. cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

### Data processing and visualization
Processing and visualization  of 16S rRNA, metagenomic and metaproteomic data were done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020; @Wilke2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020).

>>>>

\newpage
## Materials and methods
### Sampling
Leaves of *C. nodosa* were sampled in a *C. nodosa* meadow in the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20} E) and in a *C. nodosa* meadow invaded by *C. cylindracea* in the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N, \ang{13;35;42} E). Thalli of *C. cylindracea* were sampled in the same *C. nodosa* invaded meadow in the Bay of Funtana and at a locality of only *C. cylindracea* located in the proximity of the invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics and metaproteomics were collected in two contrasting seasons, on 4 December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017 (metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and metaproteomics). During spring 2018, the *C. nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved [@Najdek2020]. In addition, as not enough DNA for both metagenomic and 16S RNA analysis were obtained during the sampling on 4 December 2017, an additional sampling on 14 December 2017 was carried out in the Bay of Funtana. Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with seawater from this site. Upon arrival to the laboratory, *C. nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *C. cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

### Data processing and visualization
Processing and visualization  of 16S rRNA, metagenomic and metaproteomic data were done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020; @Wilke2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_FrontMicrobiol_2021).

@@
